---
title: "Week 3 Reflection"
author: 
  - Angel Xu
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "I use data form opendatatoronto to analyze marriage dates. I did data cleaning and tests to produce a better data for analysis."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)

data <- read_csv(here::here("cleaned_data.csv"))

```


# Introduction

I used the analysis data to analyze the number of marriage in every year from the start date to observe the change in marriage number.


# Data {#sec-mydatasection}

Data I used are all form opendatatoronto.

```{r}
#| label: fig-marriage
#| fig-cap: Bills of penguins
#| echo: false

data |> 
  ggplot(aes(x = year)) +
  geom_bar()

```

In the graph above, I used the variable year as x-axis to view the number of marriage in every year from the start date. From the bars, I can view the change in marriages.


# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this. 


## Weaknesses and next steps

The number of marriage is large and hard to see the difference.

\newpage

\appendix

# Appendix {-}


# Additional data details



\newpage


# References

